Question 1:

Resource 1: [RDocumentation](https://www.rdocumentation.org/)
Resource 2: [Codecademy](https://www.codecademy.com/learn/learn-r/modules/learn-r-introduction/cheatsheet)
BONUS: [BookDown](https://bookdown.org/ndphillips/YaRrr/logical-indexing.html)

Question 2:

Runif generates random compositions with a uniform distribution
  Example: runif.acomp(n, D), where n is the number of datasets that are to be simulated and D is the number of parts

Mean generates the average of a group of selected numbers 
  Example: mean(x) where x represents the numbers to be averaged
  
SD generates the standard deviation of values
  Example: sd(x, na.rm = FALSE) where x represents a number vector and na.rm is a logical check if missing values should be removed
  
Question 3:

```{r}
mynums <- runif(10, 0, 100)
```
mynums plot:

```{r}
plot(mynums)
```


Question 4:

```{r}
print(paste("Mean: ", mean(mynums)))
```

Question 5:

```{r}
print(paste("Standard deviation: ", sd(mynums)))

```

Question 6:

```{r}
print(mynums[1:10])
```
```{r}
mynums < mean(mynums) + sd(mynums) & mynums > mean(mynums) - sd(mynums)
```

