This doesn't work and I don't know why

---
title: "Class Exercice 2"
output: html_notebook
---

Name:  Liam Herbst
ID:  250997176


# A Data Scientist's favorite Spotify playlist

Unhappy by Spotify's recommendation engine, Rudi is thinking of developing a model that will scrape all songs from Spotify and then identify those that he would enjoy. As a first step, Rudi has labled a set of songs ("like" column) and stored the data in spotifyMusic_labledSet.csv. Given these, he wanted to know if he could develop a model to accurately predict which of the songs that are in spotifyMusic_unlabledSet.csv he would like.


Use K-Nearest Neighbors to predict which of the songs in spotifyMusic_unlabledSet.csv will Rudi like. 

```{r}
# Read the data into R
m_labled <- read.csv("spotifyMusic_labledSet.csv", header = TRUE)
m_unlabled <- read.csv("spotifyMusic_unlabledSet.csv", header = TRUE)
# Set labled$like to factor
m_labled$like <- as.factor(m_labled$like)
head(m_labled)
head(m_unlabled)
```
```{r}
# Normalize all the attributes
m_labled$acousticness = (m_labled$acousticness-mean(m_labled$acousticness))/sd(m_labled$acousticness)
m_labled$danceability = (m_labled$danceability-mean(m_labled$danceability))/sd(m_labled$danceability)
m_labled$energy = (m_labled$energy-mean(m_labled$energy))/sd(m_labled$energy)
m_labled$instrumentalness = (m_labled$instrumentalness-mean(m_labled$instrumentalness))/sd(m_labled$instrumentalness)
m_labled$liveness = (m_labled$liveness-mean(m_labled$liveness))/sd(m_labled$liveness)
m_labled$loudness = (m_labled$loudness-mean(m_labled$loudness))/sd(m_labled$loudness)
m_labled$speechiness = (m_labled$speechiness-mean(m_labled$speechiness))/sd(m_labled$speechiness)
m_labled$tempo = (m_labled$tempo-mean(m_labled$tempo))/sd(m_labled$tempo)
m_labled$valence = (m_labled$valence-mean(m_labled$valence))/sd(m_labled$valence)

# Display the first 6 elements of the standardized data
head(m_labled)
```
```{r}
# Compute the K-Fold Cross Validation to Identify the best K value
for(iter in 1:10)
{
# initialize a vector to store all the errors
  AllErrors=c()

  for(fold in 1:50)
  {
    # m_labled = training set; m_unlabled = testing set
    
    # Get the features of the training set
    trainingfeatures <- subset(m_labled, select=c(-like))
    # Get the labels of the training set
    traininglabels <- m_labled$like
    # Get the features of the testing set
    testingfeatures <- subset(m_unlabled, select=c(-like))
    
    # Load the classification library
    library(class)
    # Run PRedictions
    predictions = knn(trainingfeatures,testingfeatures,traininglabels,k=iter)
    # Display the predictions
    head(predictions)
  
    #Calculate the error
    SizeTest=dim(m_unlabled)[1]
    error = sum(predictions != m_unlabled$like)
    misclassification_rate=error/SizeTest
    AllErrors[fold] = mse
  }
  print(mean(AllErrors))
}
```
```{r}
# Display actual labels
m_labled$like
```

```{r}
# Get the number of data points in the test set
sizeTestSet = dim(m_unlabled)[1]
# Get the number of data points that are misclassified
error = sum(predictedLabels != m_unlabled$like)
# Calculate the misclassification rate
misclassification_rate = error/sizeTestSet
# Display the misclassification rate
print(misclassification_rate)
```
I've made an error and don't have time to correct. 