Read the data stored in ads.csv
```{r}
# Read CSV into R
OnlineAdsData <- read.csv("~/documents/hba2/data_science/class6/ads.csv", header = TRUE)
# Display the first few elements of the data to make sure that data is read
head(OnlineAdsData)
```

Let's create a new variable age group (<18, 18 24, 25 34, 35 44, 45 54, 55 64, 65+). For that, first create a vector of the intervals (<18, 18 24, 25 34, 35 44, 45 54, 55 64, 65+), i.e. (-Inf,0,18,24,34,44,54,64,Inf)
#Inf = Infinity

```{r}
intervals = c(-Inf,0,18,24,34,44,54,64,Inf)
intervals
```

Create a new column age_group and initialize it to 0
```{r}
OnlineAdsData$age_group = 0
head(OnlineAdsData)
```

Assign to each datat point, the appropriate age group
```{r}
OnlineAdsData$age_group <-cut(OnlineAdsData$Age, intervals)
head(OnlineAdsData)
```

Transform Gender into a readable label (female, male)
```{r}
OnlineAdsData$Gender = factor(OnlineAdsData$Gender, levels = c(0,1), labels = c("Female", 'Male'))
```

Display Summary Statistics
```{r}
summary(OnlineAdsData)
```

Get the data with Age = 0 and look at the Gender

```{r}
DataWithAge0 <- which(OnlineAdsData$Age==0)
SelectDataWithAge0 <- OnlineAdsData[DataWithAge0, ]
summary(SelectDataWithAge0)
```

Conclusion:
We need to remove the data entries (rows) where Age == 0.
Once those entries are removed, we'll be able to successfully interpret the Impressions/Clicks for each Age cluster and Gender (although we don't know which gender is which (since we recieved a binary classification with no additional information (see line 31)))

Side note (for line 45):
Square brackets mean the number is inclusive but round brackets mean the number is exclusive.

Extra:

Create a histogram for the number of impressions
```{r}
hist(OnlineAdsData$Impressions, col='black')
```

